Simulations

### 2020-12-09 Simulations.Rmd
fix
moved teamquality drawing to each season as it should be!

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(ggplot2)
library(plyr)
set.seed(400)
```

@@

# The Model
```{r, set.seed(400)}
# There are three key parameters: the probability that the worst team in the league beats the best team in a random game (given by 'p'), the standard deviation in game-to-game performance levels for each team (given by 'tao'), and the standard deviation in the team talent levels (given by 'sigma'). We as the researchers choose a value for p or the ratio of tao and sigma.
p = 0.25
tao = 4.28
sigma = 1

# Draw a "team quality" value for all teams.
teamQuality <- rnorm(30, 0, sigma)

@@

# Simulating a season
```{r}
simulateSeason <- function() {
  # Create overall games matrix with format:
  # GAME | TEAM 1 | TEAM 2 | GAMMA 1 | GAMMA 2 | GAMMA 1 - GAMMA 2 | OUTCOME 1 | OUTCOME 2
  # Where 'outcome' is the number of points awarded to their respective teams
  games <- list(seq(1, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
library(ggplot2)
library(plyr)
```

@@

# The Model
```{r}
set.seed(400)
# There are three key parameters: the probability that the worst team in the league beats the best team in a random game (given by 'p'), the standard deviation in game-to-game performance levels for each team (given by 'tao'), and the standard deviation in the team talent levels (given by 'sigma'). We as the researchers choose a value for p or the ratio of tao and sigma.
p = 0.25
tao = 4.28
sigma = 1

@@

# Simulating a season
```{r}
simulateSeason <- function() {
  # Draw a "team quality" value for all teams.
  teamQuality <- rnorm(30, 0, sigma)

  # Create overall games matrix with format:
  # GAME | TEAM 1 | TEAM 2 | GAMMA 1 | GAMMA 2 | GAMMA 1 - GAMMA 2 | OUTCOME 1 | OUTCOME 2
  # Where 'outcome' is the number of points awarded to their respective teams
  games <- list(seq(1, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]))
